\Large Plotting the Single-Electron Solution to Schr\"{o}dinger's Equation with OpenCL

### 2010-05-06 paper/paper.tex
More plots
Clear up some things

Once computation has completed, the buffer is copied back from video memory to system memory (or, if the program was running on the CPU, this step is skipped --- this is the primary overhead incurred by the use of GPU computation). There, pixel values are scaled linearly so that the brightest pixel is 100\% white.

@@

One can see in figure \ref{fig:strongPlotTwo} that this implementation is strongly scalable; the speedup is almost perfectly linear as the core count increases. It should be noted that since the 4890 only has a maximum of 50 compute units, the linear increase is only maintained until we reach 50 cores; after that, the performance gains plateau as they should.

@@

@@

\begin{figure}
    \includegraphics[width=84.5mm]{transistorPlot.pdf}
    \caption{Samples per second per million transistors with a fixed resolution ($500\times500$); larger values are better}
    \label{fig:transistorPlot}
\end{figure}

>>>>

Once computation has completed, the buffer is copied back from working memory (either video memory or system memory) to the final image buffer in system memory. Once there, pixel values are scaled linearly so that the brightest pixel is 100\% white.

@@

One can see in figure \ref{fig:strongPlotTwo} that this implementation is strongly scalable; the speedup is almost perfectly linear as the core count increases. It should be noted that since --- for our kernel --- the 4890 only has 50 compute units, the linear increase is only maintained until we reach 50 cores; after that, the performance gains plateau as they should.

@@

\subsection{Communication Overhead}

\begin{figure}
    \includegraphics[width=84.5mm]{overheadPlot.pdf}
    \caption{Overhead from image buffer copy as a percentage of the total runtime, lower numbers are better}
    \label{fig:overheadPlot}
\end{figure}

The algorithm we implemented for this project required no communication between  cores whatsoever during the course of the computation. The primary overhead involved in the entire process is the single copy of the $n\times n$ output buffer from working memory into system memory, where it is then normalized, compressed, and output (we don't consider these parts of the process when measuring performance or overhead, as they're written in Python, a language not known for its performance characteristics).

The overhead incurred during this copy can be seen in the chart in figure \ref{fig:overheadPlot} to be negligible --- in the range of a ten-thousandth of a percent of the total runtime when working on the GPU, and a one-hundred-thousandth of a percent when working on the CPU, where the data has a shorter distance to travel.

@@
